Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Recovery, and Limits to Cosmology

### 2016-05-05 ms.tex
more casey edits

Figure~\ref{fig: oii sdss} illustrates this process. The numbered boxes in the left panel show two bins ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$) in the CMD of $0.05 < z < 0.2$ SDSS galaxies. The right panel shows the Log [\ion{O}{ii}] luminosity distribution functions, $p($[\ion{O}{ii}]$| M_r, g-r)$, which we use to assign [\ion{O}{ii}] luminosity to each object. The luminosity is then converted into an [\ion{O}{ii}] flux through 
\begin{equation}
	F = \frac{L}{4\pi D_L}
\end{equation}
where $D_L$ is the luminosity distance \citeeg{Hogg2010}.

@@

To investigate this, we select cluster halo and galaxy catalogs from the Millennium simulation \citep{Springel2005a} obtained via querying the Millennium online database\footnote{http://gavo.mpa-garching.mpg.de/Millennium/} \citep{Lemson2006}. The Millennium simulation tracks $2160^3$ dark matter particles of $8.6\times 10^8 ~h^{-1}$ \Msol\ inside a comoving 500 $(h^{-1} \mathrm{Mpc})^3$ box from $z=127$ to 0. It adopts a flat cosmological model based of the values derived from the Two-degree Field Galaxy Redshift Survey \citep{Colless2001} and the first year data of the \emph{Wilkinson Microwave Anisotropy Probe} (WMAP; \citealt{Spergel2003}): $\Omega_\Lambda = 0.75$, $\Omega_M = 0.25$, $\sigma_8 = 0.9$, $n_s = 1$ and $H_0= 73$ \kms \mpc.

The halo catalogs are created using a friends-of-friends algorithm \citeeg{Turner1976} with linking length, $b=0.2$. The halos are populated with galaxies using a semi-analytical model described in \cite{Croton2006, DeLucia2006, DeLucia2007a}.

We select 4806 clusters, comprised of 623663 galaxies, at $0.02 < z < 0.5$ and $M > 10^{13}$ \Msol, and apply the same data processing as with the Buzzard galaxies. We begin by assigning each galaxy an [\ion{O}{ii}] flux value (see Section \ref{sec: oii luminosity}), and ``observe'' each galaxy using realistic (see Section \ref{sec: observations}) observational limits. After recovering 3750 clusters which have at least five galaxies observed, we calculate the LOSVD of each cluster as in Section \ref{sec: LOSVD}.

@@

Cluster masses are assigned using the ML methods (see Section \ref{sec:machine learning method}) using two different training sets. We use the full set of clusters detected in the Buzzard catalogs (14000 clusters with $M > 10^{11}$ \msol) and a training-testing split of the Millennium clusters. The top panel of Figure \ref{fig: mill buzz comparison} shows the ML predicted cluster masses as a function of true cluster mass for the $\sim$4000 Millennium clusters with the two different training sets. The median (solid and dashed lines) predicted cluster masses show similar trends regardless of the training data set used. Figure \ref{fig: mill buzz comparison}'s bottom panel show the fraction error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass. The large amount of scatter (the shaded area) in the fractional error for the Buzzard trained predictions is due to the training set including clusters with masses below the $M = 10^{13}$ \Msol\ threshold for the Millennium clusters. This allows the ML method to predict masses which can be significantly different, whereas the Millennium training set does not include $M < 10^{13}$ \Msol\ clusters, which reduces the scatter of the predicted masses.

@@

\subsection{Impact on Cluster Cosmology}

@@

To get a sense of how well HETDEX will be able to constrain cosmological parameters we follow the discussion of \cite{Weinberg2013}, and begin with a few simplifying assumptions. While sensitive to $\Omega_m$, the number density of clusters do not necessarily provide the strongest contraint, so we assume that some combination of other data sets (\eg, CMB, BAO, supernovae, WL, etc.) will constrain $\Omega_m$ to higher precision than is possible with clusters alone.

To estimate the error associated with a measurement of $\sigma_8h^{-1}$ (which \citealt{Weinberg2013} refer to as $\sigma_{11,abs}$), \cite{Weinberg2013} consider two sources of uncertainty, the systematic uncertainties in cluster mass calibration and the statistical uncertainty in the observed number density of clusters. The authors combine these two uncertainties though (their Eq. 141):
\begin{equation}
\Delta \ln \sigma_8h^{-1}(z) \approx q(z)\times 
        \max\left[ \Delta \ln M, \alpha(z)^{-1} \Delta \ln N \right].
\label{eq:sigElapprox}
\end{equation}
where $q$ is the degeneracy exponent between $\sigma_8h^{-1}$ and $\Omega_m$, $\Delta \ln M$ is the mass scale uncertainty, $\Delta \ln N$ is the cluster statistical uncertainty, and $\alpha$ is slope of the cumulative HMF. Using the \cite{Tinker2008} HMF at $z\sim0.2$ and a limiting cluster mass of $10^{14}$ \Msol, \cite{Weinberg2013} estimate $q\sim0.4$, $\alpha\sim3$, and find that any cluster survey with more than 10-20 clusters is dominated by the uncertainty in the overall mass scale.

For a survey such as HETDEX, we can estimate the constraints on $\sigma_8h^{-1}$ using Equation \ref{eq:sigElapprox}. Considering clusters with masses above $10^{14}$ \Msol, with Perfect knowledge, and the ML based cluster mass estimates the mass scale uncertainty (given in Table~\ref{tbl:mass scatter}) is reduced to $\sim 0.075$ dex or about 20\%. This gives a uncertainty on $\sigma_8h^{-1}$ of 7\%. For clusters above $10^{14}$ \Msol, Survey observations can constrain the masses to about 51\% which, in turn, constrains $\sigma_8h^{-1}$ to 20\%.

Because of the simplifying assumptions, and the superior quality of the data (no contamination, signal-to-noise issues, etc.), realistic expectations for HETDEX is to directly constrain $\sigma_8h^{-1}$ to better precision than other methods (\eg, CMB, WL, X-ray) seems bleak. For example, \cite{deHaan2016} constrain $\sigma_8h^{-1}$ to $\sim5$\% using a sample of 337 SZE detected clusters from the SPT-SZE survey. For the $\sim1500$ clusters detected with Survey observations to constrain $\sigma_8h^{-1}$ and to be dominated by cluster statistics alone ($\Delta \ln N \sim N^{-1/2}$), the absolute cluster calibration would need to be better than 2.5\%. For a fully Targeted survey, about 14000 clusters, this cluster mass calibration uncertainty reduces to $>1\%$.

@@

@@

The Buzzard cluster catalogs do not contain measurements of $\lambda$, so we supplement it by generating richnesses based on the true cluster masses. For testing we assume two versions of the richness-mass relationship. \cite{Farahi2016} base the relation on stacked velocity dispersions, and \cite{Simet2016} use weak lensing measurements to construct their relation. Because we are investigating HETDEX's ability to recover the underlying scatter in the mass-richness relationship, we use the true cluster masses perturbed by a known amount to estimate the observed richness.

As a check, after generating richness values we calculate the scatter of the masses at fixed $\lambda$, $\sigma_{M|\lambda}$ by comparing the true, unperturbed cluster masses against the richness and find that we do recover the expected scatter. We repeat the process with both assumed richness-mass relationships and recover the expected scatter in both instances.

Figure \ref{fig:mass richness} summarizes the main results of this investigation. The top panel shows the generated optical richness, $\lambda$, versus the predicted cluster mass. The cluster masses are the $ML_{\sigma, z, N_{gal}}$ based and correspond to the Targeted and Survey observation strategies. The bottom panel of Figure \ref{fig:mass richness} shows the scatter in the predicted cluster masses at fixed richness, $\sigma_{M|\lambda}$. The solid line represents the intrinsic amount of scatter added to the masses. The cluster masses are binned in increasing ten richness intervals ($10-20$, $20-30$, etc.). The inset upper panel shows the intrinsic scatter versus the recovered average scatter at fixed richness, $\langle \sigma_{M|\lambda} \rangle$ and illustrates how well the two observation strategies recover the intrinsic scatter.

We exclude clusters with $\lambda>130$ both because there are very few of them which does not accurately reproduce a scatter and because the observational studies which we base our richnesses on do not include these clusters. We find that we are able to accurately recover an average intrinsic scatter of $0.2 <\langle \sigma_{M|\lambda} \rangle <0.3$ dex, finding $\langle \sigma_{M|\lambda} \rangle = 0.255\pm{0.02}$ at $\sigma_{true} = 0.25$ with Survey observations. This is very promising as other observational studies have estimated the intrinsic scatter of real clusters to be $\sim0.25$ dex \citeeg{Rozo2014, Rozo2015}. As the intrinsic scatter increases or decreases, we fail to recover the scatter as accurately.

To get an idea of how well HETDEX will constrain the absolute mass scale we can find the best fitting relation to our richness-mass data. To generate the best fitting lines we follow the general procedure of \cite{Hogg2010}, by defining an objective function and then minimizing the loss. Our objective function is
\begin{equation}\label{eq:objectivei}
p(y_i|x_i,\sigma_{yi},m,b,\sigma) = \frac{1}{\sqrt{2\,\pi\,(\sigma_{yi}^2+\sigma^2)}}
 \,\exp\left(-\frac{[y_i - m\,x_i - b]^2}{2\,(\sigma_{yi}^2+\sigma^2)}\right)
\end{equation}
where we consider both measurement errors in $y_i$, $\sigma_{yi}$, and intrinsic scatter, $\sigma$, in the relation between $x_i$ and $y_i$. We assume that the intrinsic scatter is constant from point to point and that all of the measurement errors are Gaussian. We convert this objective function into a likelihood by multiplying all of the individual probabilities together,  
\begin{equation}\label{eq:like}
\mathscr{L} = \prod_{i=1}^N \ p(y_i|x_i,\sigma_{yi},m,b, \sigma).
\end{equation}
We again rely on MCMC samples to sample the posterior probability distribution and thus maximize the likelihood. The best fitting slope and intercept are quoted as the median value of the posterior probability distribution with 68\% error bars defined as the 16th and 84th percentiles of the same distribution.

For a richness-mass relation with an intrinsic scatter of $\langle \sigma_{M|\lambda} \rangle = 0.25$, and following the more traditional parameterization of the richness-mass relation \citeeg{Rykoff2012, Farahi2016}, we find a best-fitting relation for the Targeted observations as
\begin{equation}
	\ln\bigg{(}\frac{M_{200c}}{h_{70}^{-1} 10^{14}\Msol}\bigg{)} = 0.09\pm0.01 + 0.90\pm0.01 \ln\bigg{(}\frac{\lambda}{60}\bigg{)}
\end{equation}
and the Survey observations as
\begin{equation}
	\ln\bigg{(}\frac{M_{200c}}{h_{70}^{-1} 10^{14}\Msol}\bigg{)} = 0.31\pm0.02 + 0.77\pm0.02 \ln\bigg{(}\frac{\lambda}{60}\bigg{)}.
\end{equation}
This gives $M_{200c} = (1.09\pm0.01)\times10^{14} h^{-1}$ \Msol  and  $M_{200c} = (1.36\pm0.03)\times10^{14}h^{-1}$ \Msol\ at $\lambda=40$ for the Targeted and Survey observations respectively. If the intrinsic scatter is reduced to $\sim 0.05$ dex we recover an overall normalization of $M_{200c} = (1.6\pm0.02)\times10^{14} h^{-1}$ \Msol\ and $M_{200c} = (1.65\pm0.03)\times10^{14} h^{-1}$ for the Targeted and Survey observations at $\lambda=40$. In both cases, this normalization differs significantly from the $M_{200c} \approx 2.1\times10^{14} h^{-1}$ \Msol\ found in recent work by \cite{Li2016, Simet2016}.

@@

\section*{Acknowledgements}
The authors also wish to thank the anonymous referee whose comments and suggestions significantly improved both the quality and clarity of this work. We also thank Steven W. Crawford for many helpful discussions. This research made use of This research made use of the {\sc IPython} package \citep{Perez2007} and {\sc matplotlib}, a Python library for publication quality graphics \citep{Hunter2007}. Figure \ref{fig: probability corner} is heavily based on \cite{Foreman-Mackey2016}. Funding for the SDSS and SDSS-II has been provided by the Alfred P. Sloan Foundation, the Participating Institutions, the National Science Foundation, the U.S. Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England. The SDSS Web Site is http://www.sdss.org/. The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions.

>>>>

Figure~\ref{fig: oii sdss} illustrates this process. The numbered boxes in the left panel show two bins ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$) in the CMD of $0.05 < z < 0.2$ SDSS galaxies. The right panel shows the Log [\ion{O}{ii}] luminosity distribution functions, $p($[\ion{O}{ii}]$| M_r, g-r)$, which we use to assign [\ion{O}{ii}] luminosity to each object. The luminosity is then converted into an [\ion{O}{ii}] flux through 
\begin{equation}
	F = \frac{L}{4\pi D_L}
\end{equation}
where $D_L$ is the luminosity distance \citeeg{Hogg1999}.

@@

We turn to the Millennium simulation where the underlying cosmological assumptions differ substantially from Buzzard. The Millennium simulation adopts a flat cosmological model based of the values derived from the Two-degree Field Galaxy Redshift Survey \citep{Colless2001} and the first year data of the \emph{Wilkinson Microwave Anisotropy Probe} (WMAP; \citealt{Spergel2003}): $\Omega_\Lambda = 0.75$, $\Omega_M = 0.25$, $\sigma_8 = 0.9$, $n_s = 1$ and $H_0= 73$ \kms \mpc. The clusters in Millennium provide a testing sample to understand how a training sample derived from Buzzard will impact the mass recovery on a wholly new dataset.

We repeat our analysis using cluster halo and galaxy catalogs from the Millennium simulation \citep{Springel2005a} obtained via querying the Millennium online database\footnote{http://gavo.mpa-garching.mpg.de/Millennium/} \citep{Lemson2006}. The Millennium simulation tracks $2160^3$ dark matter particles of $8.6\times 10^8 ~h^{-1}$ \Msol\ inside a comoving 500 $(h^{-1} \mathrm{Mpc})^3$ box from $z=127$ to 0. The halo catalogs are created using a friends-of-friends algorithm \citeeg{Turner1976} with linking length, $b=0.2$. The halos are populated with galaxies using a semi-analytical model described in \cite{Croton2006, DeLucia2006, DeLucia2007a}.

We select 4806 clusters, comprised of 623,663 galaxies, at $0.02 < z < 0.5$ and $M > 10^{13}$ \Msol, and apply the same data processing as with the Buzzard galaxies. We begin by assigning each galaxy an [\ion{O}{ii}] flux value (see Section \ref{sec: oii luminosity}), and ``observe'' each galaxy using realistic (see Section \ref{sec: observations}) observational limits. After recovering 3750 clusters which have at least five galaxies observed, we calculate the LOSVD of each cluster as in Section \ref{sec: LOSVD}.

@@

We conduct our test in two ways. Both use the ML methods (see Section \ref{sec:machine learning method}) to predict the cluster masses of the Millennium clusters, but each test uses a different training set. First, we use the full set of clusters detected in the Buzzard catalogs (14,000 clusters with $M > 10^{11}$ \msol) to train the ML. Second, the Millennium clusters are split into training-testing samples. This provides a test case where we have different cosmological choices between the training and testing samples, and the same cosmological assumptions in both samples.

The top panel of Figure \ref{fig: mill buzz comparison} shows the ML predicted cluster masses for the $\sim$4000 Millennium clusters as a function of true cluster mass. The orange (Millennium) and green (Buzzard) colors indicate the two different training samples. The median (solid and dashed lines) predicted cluster masses show similar trends regardless of the training data set used. Figure \ref{fig: mill buzz comparison}'s bottom panel shows the fraction error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass. The large amount of scatter (the shaded area) in the fractional error for the Buzzard trained predictions is due to the training set including clusters with masses below the $M = 10^{13}$ \Msol\ threshold for the Millennium clusters. This allows the ML method to predict masses which can be significantly different, whereas the Millennium training set does not include $M < 10^{13}$ \Msol\ clusters, which reduces the scatter of the predicted masses.

@@

\subsection{Constraints on Cosmological Parameters}

@@

To get a sense of how well HETDEX will be able to constrain cosmological parameters we follow the discussion of \defcitealias{Weinberg2013}{W13}\cite{Weinberg2013} (hereafter \citetalias{Weinberg2013}), and begin with a few simplifying assumptions. While sensitive to $\Omega_m$, the number density of clusters does not necessarily provide the strongest contraint, so we assume that some combination of other data sets (\eg, CMB, BAO, supernovae, WL, etc.) will constrain $\Omega_m$ to higher precision than is possible with clusters alone.

To estimate the error associated with a measurement of $\sigma_8h^{-1}$ (which \citetalias{Weinberg2013} refer to as $\sigma_{11,abs}$), \citetalias{Weinberg2013} consider two sources of uncertainty, the systematic uncertainties in cluster mass calibration and the statistical uncertainty in the observed number density of clusters. The authors combine these two uncertainties though (their Eq. 141):
\begin{equation}
\Delta \ln \sigma_8h^{-1}(z) \approx q(z)\times 
        \max\left[ \Delta \ln M, \alpha(z)^{-1} \Delta \ln N \right].
\label{eq:sigElapprox}
\end{equation}
where $q$ is the degeneracy exponent between $\sigma_8h^{-1}$ and $\Omega_m$, $\Delta \ln M$ is the mass scale uncertainty, $\Delta \ln N$ is the cluster statistical uncertainty, and $\alpha$ is slope of the cumulative HMF. Using the \cite{Tinker2008} HMF at $z\sim0.2$ and a limiting cluster mass of $10^{14}$ \Msol, \citetalias{Weinberg2013} estimate $q\sim0.4$, $\alpha\sim3$, and find that any cluster survey with more than 10-20 clusters is dominated by the uncertainty in the overall mass scale.

For a survey such as HETDEX, we can estimate the constraints on $\sigma_8h^{-1}$ using Equation \ref{eq:sigElapprox}. Considering clusters with masses above $10^{14}$ \Msol, with Perfect knowledge, and the ML based cluster mass estimates the mass scale uncertainty (given in Table~\ref{tbl:mass scatter}) is reduced to $\Delta_{log_{10}}M \sim 0.075$ dex or about 20\%. This gives a uncertainty on $\sigma_8h^{-1}$ of 7\%. For clusters above $10^{14}$ \Msol, Survey observations can constrain the masses to about 51\% which, in turn, constrains $\sigma_8h^{-1}$ to 20\%.

Because of the simplifying assumptions, and the superior quality of the data (no contamination, signal-to-noise issues, etc.), realistic expectations for HETDEX is to directly constrain $\sigma_8h^{-1}$ to better precision than other methods (\eg, CMB, WL, X-ray) seems bleak. For example, \cite{deHaan2016} constrain $\sigma_8h^{-1}$ to $\sim5$\% using a sample of 337 SZE detected clusters from the SPT-SZE survey. For the $\sim1500$ clusters detected with Survey observations to constrain $\sigma_8h^{-1}$ and to be dominated by cluster statistics alone ($\Delta \ln N \sim N^{-1/2}$), the absolute cluster calibration would need to be better than 2.5\%. For a fully Targeted survey, about 14,000 clusters, this cluster mass calibration uncertainty reduces to $>1\%$.

@@

The Buzzard cluster catalogs do not contain measurements of $\lambda$, so we supplement it by generating richnesses based on the true cluster masses. For testing we assume two versions of the richness-mass relationship. \cite{Farahi2016} base the relation on stacked velocity dispersions, and \cite{Simet2016} use weak lensing measurements to construct their relation. Because we are investigating HETDEX's ability to recover the overall cluster mass scale and underlying scatter in the mass-richness relationship, we use the true cluster masses perturbed by a known amount to estimate the observed richness.

To confirm that measuring the underlying scatter is possible, after generating richness values we calculate the scatter of the cluster masses at fixed $\lambda$, $\sigma_{M|\lambda}$, by comparing the true, unperturbed cluster masses against the richness and find that we do recover the expected scatter. We repeat the process with both assumed richness-mass relationships and recover the expected scatter in both instances.

Primarily, we are interested in the intrinsic scatter of the richness-mass relationship. This is because HETDEX is uniquely situated to estimate the scatter, whereas studies rely on stacked data \citeeg{Farahi2016,Simet2016} lose that information. However, for technical reasons we begin by estimating how well HETDEX will constrain the absolute mass scale (something stacked studies excel at). As part of our fitting process to constrain the mass scale, we estimate the overall scatter in the relationship, so it makes sense to begin here.

To get an idea of how well HETDEX will constrain the absolute mass scale, we can find the best fitting relation to our richness-mass data. To generate the best fitting lines we follow the general procedure of \cite{Hogg2010}, by defining an objective function and then minimizing the loss. Our objective function is
\begin{equation}\label{eq:objectivei}
p(y_i|x_i,\sigma_{yi},m,b,\sigma) = \frac{1}{\sqrt{2\,\pi\,(\sigma_{yi}^2+\sigma^2)}}
 \,\exp\left(-\frac{[y_i - m\,x_i - b]^2}{2\,(\sigma_{yi}^2+\sigma^2)}\right)
\end{equation}
where $y_i$ is the observed cluster mass, $x_i$ is the observed richness, $\sigma_{yi}$ is the uncertainty in observed cluster mass, $m$ is the power law slope, $b$ is the overall cluster mass scale, and $\sigma$ is the intrinsic scatter between richness and cluster mass. We assume that the intrinsic scatter is constant from point to point and that all of the measurement errors are Gaussian. We convert this objective function into a likelihood by multiplying all of the individual probabilities together,  
\begin{equation}\label{eq:like}
\mathscr{L} = \prod_{i=1}^N \ p(y_i|x_i,\sigma_{yi},m,b, \sigma).
\end{equation}
We again rely on MCMC samples to sample the posterior probability distribution and thus maximize the likelihood. The best fitting slope and intercept are quoted as the median value of the posterior probability distribution with 68\% error bars defined as the second moment of the same distribution.

We limit our clusters to those with $10 \leq \lambda < 130$ in our fitting analysis because there are very few clusters with $\lambda>130$ and to better coincide with other observational studies \citeeg{Saro2015}. For a richness-mass relation with an intrinsic scatter of $\langle \sigma_{M|\lambda} \rangle = 0.25$ dex, we find a best-fitting relation for the Targeted observations as
\begin{equation}
	\mathrm{Log}\ M_{200c}/\Msol = 12.54\pm0.02 + 0.97\pm0.02\ \mathrm{Log}\ \lambda
\end{equation} 
and the Survey observations as
\begin{equation}
	\mathrm{Log}\ M_{200c}/\Msol = 12.78\pm0.04 + 0.86\pm0.03\ \mathrm{Log}\ \lambda
\end{equation} 
This gives $M_{200c} = (1.22\pm...)\times10^{14}$ \Msol and $M_{200c} = (1.44\pm...)\times10^{14}$ \Msol\ at $\lambda=40$ for the Targeted and Survey observations respectively. In both cases, this normalization differs significantly from the $M_{200c} \approx 2.1\times10^{14} h^{-1}$ \Msol\ found in recent work \cite{Li2016, Simet2016}. If the intrinsic scatter is reduced to $\sim 0.05$ dex we recover an overall normalization of $M_{200c} = (1.8\pm...)\times10^{14}$ \Msol\ and $M_{200c} = (1.78\pm...)\times10^{14}$ for the Targeted and Survey observations at $\lambda=40$.

The intrinsic scatter is also estimated during the fitting process. For observations with a richness-mass relation intrinsic scatter of $\langle \sigma_{M|\lambda} \rangle = 0.25$ dex, we recover $\langle \sigma_{M|\lambda} \rangle = 0.22\pm0.003$ dex and $\langle \sigma_{M|\lambda} \rangle = 0.20\pm0.01$ dex for Targeted and Survey observations respectively. The discrepancy between the intrinsic value and the measured value is due to the uncertainties in the individual cluster mass predictions. As the prediction intervals are narrowed, the recovered intrinsic scatter approaches the true value. For example, with cluster mass prediction intervals half the size of the current intervals we measure $\langle \sigma_{M|\lambda} \rangle$ to be $\sim 0.25$ and $\sim 0.23$ for the two sets of observations.

@@

Figure \ref{fig:mass richness} summarizes the main results of this investigation. The top panel shows the generated optical richness, $\lambda$, versus the predicted cluster mass. The cluster masses are the $\mathrm{ML}_{\sigma, z, N_{gal}}$ based and correspond to the Targeted and Survey observation strategies. The bottom panel of Figure \ref{fig:mass richness} shows the scatter in the predicted cluster masses at fixed richness, $\sigma_{M|\lambda}$. The solid line represents the intrinsic amount of scatter added to the masses. The cluster masses are binned in increasing ten richness intervals ($10-20$, $20-30$, etc.). The inset upper panel shows the intrinsic scatter versus the recovered average scatter at fixed richness, $\langle \sigma_{M|\lambda} \rangle$ and illustrates how well the two observation strategies recover the intrinsic scatter.

 We find that we are able to accurately recover an average intrinsic scatter of $0.2 <\langle \sigma_{M|\lambda} \rangle <0.3$ dex, finding $\langle \sigma_{M|\lambda} \rangle = 0.255\pm{0.02}$ at $\sigma_{true} = 0.25$ with Survey observations. This is very promising as other observational studies have estimated the intrinsic scatter of real clusters to be $\sim0.25$ dex \citeeg{Rozo2014, Rozo2015}. As the intrinsic scatter increases or decreases, we fail to recover the scatter as accurately.

@@

\section*{Acknowledgements}
The authors also wish to thank the anonymous referee whose comments and suggestions significantly improved both the quality and clarity of this work. We also thank Steven W. Crawford for many helpful discussions. This research made use of This research made use of the {\sc IPython} package \citep{Perez2007} and {\sc matplotlib}, a Python library for publication quality graphics \citep{Hunter2007}. Figure \ref{fig: probability corner} is heavily based on \cite{Foreman-Mackey2016}. Funding for the SDSS and SDSS-II has been provided by the Alfred P. Sloan Foundation, the Participating Institutions, the National Science Foundation, the U.S. Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England. The SDSS Web Site is http://www.sdss.org/.
